API design for machine learning software: experiences from the scikit-learn project

### 2013-06-22 paper.tex

A distinguishing feature of the \sklearn API is its ability to
compose new estimators from several base estimators. Composition mechanisms can
be used to combine typical machine learning workflows into a single object which
is itself an estimator. Thanks to duck typing, composed
estimators can be used wherever usual estimators can be used. In particular,
they integrate within model selection routines, allowing one to optimize at once
every step of a complex workflow. Composition of estimators can be done in two
ways: either sequentially through \texttt{Pipeline} objects or in a parallel
fashion through \texttt{FeatureUnion} objects.

@@

To ease code reuse, simplify implementation and skip the introduction of
superfluous classes, the principle of \textit{duck typing} is exploited
throughout the codebase. This technique allows for both extensibility and
flexibility: as long as an estimator follows the API and conventions
outlined in Section~\ref{sec:core-api}, then it can be used in lieu of a
built-in estimator (e.g., it can be plugged into pipelines or grid search).
That is, estimators are defined only by interface, not by inheritance,
and external developers are not forced to inherit from any \sklearn class.

>>>>

A distinguishing feature of the \sklearn API is its ability to
compose new estimators from several base estimators. Composition mechanisms can
be used to combine typical machine learning workflows into a single object which
is itself an estimator, and can be used wherever usual estimators can be used.
In particular,
they integrate within model selection routines, allowing one to optimize at once
every step of a complex workflow. Composition of estimators can be done in two
ways: either sequentially through \texttt{Pipeline} objects or in a parallel
fashion through \texttt{FeatureUnion} objects.

@@

To ease code reuse, simplify implementation and skip the introduction of
superfluous classes, the Python principle of \textit{duck typing} is exploited
throughout the codebase. This means that estimators are defined by interface,
not by inheritance, where the interface is entirely implicit
as far as the programming language is concerned.
Duck typing allows both for extensibility and
flexibility: as long as an estimator follows the API and conventions
outlined in Section~\ref{sec:core-api}, then it can be used in lieu of a
built-in estimator (e.g., it can be plugged into pipelines or grid search)
and external developers are not forced to inherit from any \sklearn class.
